\documentclass{article}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{booktabs}

\begin{document}

\section*{Mixed Content Validation}

This scenario exercises a mixture of inline math, chemical notation, and
standard equations to verify conversion fidelity. Sampling records show
that $\mathrm{CO}_{2}$ concentration stayed below $480\,\mathrm{ppm}$ while
coolant temperature remained under $\SI{315}{\kelvin}$. The reactor outlet
flow averaged $18\,\mathrm{m}^{3}/\mathrm{s}$ and the density was
$1.25\,\mathrm{kg}/\mathrm{m}^{3}$.

We observed the daughter product $^{203}_{82}\mathrm{Pb}$ alongside the
intermediate isotope $^{99}\mathrm{Mo}$. Catalytic activity compared two
samples: $c_{\mathrm{eq},1}$ tracked reference behavior and
$c_{\mathrm{eq},2}$ monitored enriched feed. Reaction stoichiometry for
methane oxidation follows
$\mathrm{CH}_{4} + 2\,\mathrm{O}_{2} \rightarrow \mathrm{CO}_{2} + 2\,\mathrm{H}_{2}\mathrm{O}$.

\subsection*{Inline and Display Math}

Transient state estimates used the recurrence
$x_{i+1} = \alpha x_i + \beta u_i + \gamma$ with
$u_i = k_p (r_i - x_i)$. The energy balance introduced the integral

\begin{align}
E(t) &= E_0 + \int_{0}^{t} \dot{Q}(\tau)\,\mathrm{d}\tau, \\
\Phi(t) &= \exp(-\lambda t) \sin(\omega t).
\end{align}

To keep notation consistent, spectral radius constraints employed
$\rho(A) < 1$ and the variance update used
$\sigma_{k+1}^{2} = (1 - g_k h_k)\sigma_{k}^{2} + g_k^{2}\sigma_{v}^{2}$.

\subsection*{Chemical and Unit Notation}

The aqueous equilibrium constant was reported as
$K_\mathrm{eq} = \frac{[\mathrm{HCO}_{3}^{-}]\,[\mathrm{H}^{+}]}{[\mathrm{H}_{2}\mathrm{CO}_{3}]}$, while the
reaction pathway featured the intermediate HO-CH$_2$-COO$^{-}$. A secondary
analysis leveraged $^{99m}\mathrm{Tc}$ imaging, referencing the decay chain
$^{99}\mathrm{Mo} \xrightarrow{\gamma} {}^{99m}\mathrm{Tc} + \gamma$. Mass transfer coefficients
were recorded as $1.8\,\mathrm{mol}/(\mathrm{m}^{2}\,\mathrm{s})$ and diffusion
coefficients as $2.4\times10^{-9}\,\mathrm{m}^{2}/\mathrm{s}$.

\subsection*{Tabular Data}

\sisetup{table-format=2.2}
\begin{table}[h]
    \centering
    \begin{tabular}{lcr}
        \toprule
        Quantity & \multicolumn{1}{c}{Measurement} & Representation \\
        \midrule
        Density & \SI{1.25}{\kilogram\per\meter^{3}} & $1.25\,\mathrm{kg}/\mathrm{m}^{3}$ \\
        Flow rate & \SI{18}{\cubic\meter\per\second} & $18\,\mathrm{m}^{3}/\mathrm{s}$ \\
        Half-life & \SI{66}{\hour} & $^{99}\mathrm{Mo}$ sample \\
        Conductivity & \SI{5.6}{\siemens\per\meter} & $5.6\,\mathrm{S}/\mathrm{m}$ \\
        Diffusion & \num{2.4e-9} & $2.4\times10^{-9}\,\mathrm{m}^{2}/\mathrm{s}$ \\
        \bottomrule
    \end{tabular}
    \caption{Measurements mixing unit syntax and inline math.}
    \label{tab:mixed}
\end{table}

\subsection*{Enumerated Checks}

\begin{enumerate}
    \item Verify that $c_{\mathrm{eq},1}$ and $c_{\mathrm{eq},2}$ stay as
    upright text.
    \item Confirm $x_{i+1} = x_i + \Delta x$ stays in OMML math.
    \item Ensure unit fractions such as $15\,\mathrm{m}^{3}/\mathrm{s}$ render
    without italics.
    \item Check isotope notation $^{235}\mathrm{U}$ and
    $^{60}\mathrm{Co}$ remain plain text.
    \item Validate chemical ratios like
    $\frac{n_{\mathrm{CO}_{2}}}{n_{\mathrm{CH}_{4}}}$ keep subscripts upright.
\end{enumerate}

\end{document}
